Modelling at-bats in baseball using the generalised Pareto distribution

### 2023-02-16 bibat/examples/baseball/docs/report.qmd
Correct wrong path in baseball report
bump version

---
title: "Modelling at-bats in baseball using the generalised Pareto distribution"
subtitle: "A report created using bibat version 0.0.5"
author: "Teddy Groves"
bibliography: bibliography.bib
reference-location: margin
format:
  html: default
  pdf: default
filters:
  - include-code-files
---

@@

Next I wrote a file `gpareto-reg.stan`:

```{.stan include="../src/stan/gpareto-reg.stan"}
```

>>>>

---
title: "Modelling at-bats in baseball using the generalised Pareto distribution"
subtitle: "A report created using bibat version 0.0.6"
author: "Teddy Groves"
bibliography: bibliography.bib
reference-location: margin
format:
  html: default
  pdf: default
filters:
  - include-code-files
---

@@

Next I wrote a file `gpareto.stan`:

```{.stan include="../src/stan/gpareto.stan"}
```
